A Real-Time Sonar Simulator for Automatic Target Recognition

### 2019-04-18 Simulator/article.tex
Long since last commit
Simulator: End of day
2019-04-18

\newif\ifBuildBibliography\BuildBibliographytrue  % Whether to include the references.bib file or use inline references.
\newif\ifOverLeaf\OverLeaftrue                  % Using OverLeaf to edit?

@@

\RequirePackage{amsfonts}
\usepackage{cite}

@@

\usepackage{accents}

@@

\usepackage{tikz}
\usetikzlibrary{calc,positioning,shapes,snakes}
%\newcommand{\tikzmark}[1]{\tikz[remember picture]\coordinate(#1){(-.35em,-.545ex)};}
\newcommand{\tikzmark}[2]{\tikz[remember picture,baseline=(#1.base)]\node[shape=rectangle,inner sep=0pt](#1){#2};}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

\usepackage{multirow}
\usepackage{tabularx}

@@

>>>>

\newif\ifBuildBibliography\BuildBibliographytrue  % Whether to include the references.bib file or use inline references.
\newif\ifOverLeaf\OverLeaffalse                  % Using OverLeaf to edit?

@@

\RequirePackage{amsfonts}
% \usepackage[makeroom]{cancel}
% \usepackage{cancel}
% \usepackage{ulem}
\usepackage{cite}

@@

\usepackage{accents}
\usepackage{moresize}

@@

\usepackage{tikz}
\usetikzlibrary{arrows.meta,calc,positioning,shadows,shadows.blur,shapes,snakes}
%\newcommand{\tikzmark}[1]{\tikz[remember picture]\coordinate(#1){(-.35em,-.545ex)};}
\newcommand{\tikzmark}[2]{\tikz[remember picture,baseline=(#1.base)]\node[shape=rectangle,inner sep=0pt](#1){#2};}
%\newcommand{\tikzmark}[2][]{\tikz[remember picture,overlay]\coordinate[#1](#2);}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2.5pt] (char) {#1};}}

\tikzset{-{to[length=.5em,width=.5em]}}

\newcommand\step[1]{\tikz[baseline=(char.base)]{%
            \node[shape=circle,draw,color=Green,shade,top color=black!5!white,bottom color=black!15!white,inner sep=.75pt] (char) {\color{Green}#1};}}
\newcommand\figstep[2]{\step{#1}\mbox{}\hfill\parbox[t]{.97\linewidth}{#2}}

\makeatletter
\let\@oldseccntformat\@seccntformat
\DeclareRobustCommand{\@seccntformat}[1]{%
  \def\temp@@a{#1}%
  \def\temp@@b{subsubsection}%
  \ifx\temp@@a\temp@@b
  \else
  \@oldseccntformat{#1}
  \fi
}
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\parindent\step{\normalfont\arabic{subsubsection}}\enskip}{0ex plus 0.1ex minus 0.1ex}{0ex}{\normalfont\normalsize\itshape}}%
\makeatother

%\titleformat{\subsubsection}[hang]{\itshape}{\thesubsubsection}{0.6em}{}

%\makeatletter
%\xpatchcmd{\@sect}{%
%  \protected@edef\@svsec{\@seccntformat{#1}\relax}%
%}{%
%  \ifnum0=\pdfstrcmp{#1}{section}%
%  \def\@svsec{\circlednumber{\number\value{section}}\quad\relax}%
%  \else
%  \protected@edef\@svsec{\@seccntformat{#1}\relax}%
%  \fi
%  }{}{}
%\makeatother

%\titleformat{\subsubsection}{\Large\bfseries}{}{0em}{%
%\begin{picture}(0,0)
%\put(12,4){\circle{28}}
%\end{picture}\makebox[1.45em][c]{\thesubsubsection}\quad}

\usepackage{multirow}
\usepackage{tabularx}
\usepackage{collcell}
\usepackage{booktabs}
\usepackage{calc}

@@

% The below line commands ensure proper fill color along with the booktabs package
% \specialrule[width]{abovespace}{belowspace}
\colorlet{tableheadcolor}{tabBlue}
\newlength\arulesep\setlength\arulesep{\aboverulesep}
\newlength\brulesep\setlength\brulesep{\belowrulesep}
\setlength{\aboverulesep}{0pt}
\setlength{\belowrulesep}{0pt}  
\newcommand\topline{\arrayrulecolor{black}\specialrule{\heavyrulewidth}{\arulesep}{0pt}%
            \arrayrulecolor{tableheadcolor}\specialrule{\brulesep}{0pt}{0pt}%
            \arrayrulecolor{black}}
\newcommand\midline{\arrayrulecolor{tableheadcolor}\specialrule{\arulesep}{0pt}{0pt}%
            \arrayrulecolor{black}\specialrule{\lightrulewidth}{0pt}{0pt}%
            \arrayrulecolor{white}\specialrule{\brulesep}{0pt}{0pt}%
            \arrayrulecolor{black}}
\newcommand\cmidline[2][]{\arrayrulecolor{tableheadcolor}\cmidrule[\arulesep]{#2}%
                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#2}%
                        \arrayrulecolor{tableheadcolor}\cmidrule[\brulesep]{#2}%
%                         \arrayrulecolor{tableheadcolor}\cmidrule[\belowrulesep]{#1}%
%                         \vspace{-\belowrulesep}
%                         \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}
%                         \arrayrulecolor{tableheadcolor}\cmidrule[\belowrulesep]{#1}%
%                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}%\specialrule{\lightrulewidth}{0pt}{0pt}%
%                        \arrayrulecolor{white}\cmidrule[0\belowrulesep]{#1}%
                        \arrayrulecolor{black}}
%\newcommand\cbmidline[1]{\arrayrulecolor{tableheadcolor}\cmidrule[0\aboverulesep]{#1}%
%                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#1}%\specialrule{\lightrulewidth}{0pt}{0pt}%
%                        \arrayrulecolor{white}\cmidrule[0\belowrulesep]{#1}%
%                        \arrayrulecolor{black}}
%\newlength\arulesep{}\setlength\arulesep{\aboverulesep}\addtolength\arulesep{\lightrulewidth}
%\newcommand\cmidline[1]{\arrayrulecolor{tableheadcolor}\specialrule{\aboverulesep}{0pt}{-\aboverulesep}%
%            \arrayrulecolor{black}\ule{#1}
%            \arrayrulecolor{tableheadcolor}\specialrule{\belowrulesep}{-\belowrulesep}{0pt}%
%            \arrayrulecolor{black}}
%\newlength\trulesep{}\setlength  \trulesep{\aboverulesep}
%                     \addtolength\trulesep{\lightrulewidth}
%                     \addtolength\trulesep{\belowrulesep}
%\newlength\brulesep{}\setlength  \brulesep{\lightrulewidth}
%                     \addtolength\brulesep{\belowrulesep}
%\newlength\mrulesep{}\setlength  \mrulesep{\aboverulesep}
%                     \addtolength\mrulesep{\belowrulesep}
%\newcommand*{\cmidline}[1]{\cmidrule(rl){#1}}%
%                      \arrayrulecolor{tableheadcolor}\specialrule{\trulesep}{0pt}{-\trulesep}\arrayrulecolor{black}
%                      \cmidrule(rl){#1}
%%                      \arrayrulecolor{white}\specialrule{0pt}{-\mrulesep}{0pt}%
%                      \arrayrulecolor{black}
%}

%\newcommand*\cmidwrap[1]{\cmidrule(rl){#1}}%
%                      \arrayrulecolor{tableheadcolor}\specialrule{\trulesep}{0pt}{-\trulesep}\arrayrulecolor{black}
%                      \cmidrule(rl){#1}
%%                      \arrayrulecolor{white}\specialrule{0pt}{-\mrulesep}{0pt}%
%                      \arrayrulecolor{black}
%}

%             \arrayrulecolor{tableheadcolor} \specialrule{6pt}{0pt}{-6pt} \arrayrulecolor{black}
%             
%             \headcol Blue & Red & Yellow\\
%\newcommand\cmidline[1]{\arrayrulecolor{tableheadcolor}\specialrule{\aboverulesep}{0pt}{0pt}%
%                        \arrayrulecolor{black}\specialrule{\lightrulewidth}{0pt}{0pt}%
%                        \arrayrulecolor{white}\specialrule{\belowrulesep}{0pt}{0pt}%
%                        \arrayrulecolor{black}}
%            
%\cmidrule(lr){2-3}
%
%\usepackage{xparse}
%\newcommand{\cmidline}{\noalign\bgroup\CMidRuleZaux{}}
%
%\ExplSyntaxOn
%\makeatletter
%\NewDocumentCommand{\CMidRuleZaux}{
%    m % Material to reinsert before cmidrule.
%%    O{0.0ex} % #1 = left adjust
%%    O{0.0ex} % #1 = right adjust
%    m  %   #3 = columns to span
%}{
%    \peek_meaning_remove_ignore_spaces:NTF \cmidline
%      { \CMidRuleZaux { #1 \beforerule\cmidrule[\cmidrulewidth](lr){#2} } }%(l{#2}r{#3})
%      { \egroup #1 \cmidrule[\cmidrulewidth](lr){#2} }
%}
%\makeatother
%\ExplSyntaxOff
%
%                     
%\newcommand*\beforerule{\arrayrulecolor{tableheadcolor}\specialrule{\trulesep}{0pt}{-\trulesep}\arrayrulecolor{black}}
%\newcommand*\afterrule{\arrayrulecolor{white}\specialrule{0pt}{-\mrulesep}{0pt}\arrayrulecolor{black}}

\newlength\trulesep{}\setlength  \trulesep{\arulesep}
                     \addtolength\trulesep{\lightrulewidth}
                     \addtolength\trulesep{\brulesep}
\newcommand\cmidwrap[1]{%\arrayrulecolor{tableheadcolor}\specialrule{\trulesep}{0pt}{-\trulesep}%
                        \arrayrulecolor{tableheadcolor}\specialrule{\arulesep}{0pt}{0pt}%
                        \arrayrulecolor{tableheadcolor}\specialrule{\lightrulewidth}{0pt}{-\lightrulewidth}%
%                        \arrayrulecolor{black}\cmidrule[\lightrulewidth]{#2}%
%                        \arrayrulecolor{tableheadcolor}\cmidrule[\brulesep]{#2}%
                        \arrayrulecolor{black}#1
                        \arrayrulecolor{tableheadcolor}\specialrule{\brulesep}{0pt}{0pt}%
%            \setlength{\aboverulesep}{10pt}
%            \setlength{\belowrulesep}{10pt}
%            #1
            }
